### 2013-07-06 cws/emnlp_cws/discussion.tex
final edits
a bunch of final minor changes

%%some errors where DD picks the wrong model:
%%gold: 有 亭台樓閣 流水
%%CRF: 亭台 樓閣  <-- DD
%%PCT: 亭台樓閣
%\begin{small}
%\begin{tabbing}
%\ \ \ \ \= \emph{Gloss}\ \ \ \ \= Large-scale / sea, land, and air / \\ 
%\> \> joint / military exercises\\
%\> \emph{Gold}\> 大规模 / 海陆空 / 联合 / 军演\\
%
%\> \emph{CRF}\> 大规模 / 海 / 陆空 / 联合 / 军演\\
%
%\> \emph{PCPT}\> 大规模 / 海陆空 / 联合 / 军演\\
%
%\> \emph{DD}\> 大规模 / 海 / 陆空 / 联合 / 军演\\
%\end{tabbing}
%\end{small}
In many cases the relative confidence of each model means that dual decomposition is capable of using information from both sources to generate a series of correct segmentations better than either baseline model alone. The example below shows a difficult-to-segment proper name comprised of common characters, which results in undersegmentation by the character-based CRF and oversegmentation by the word-based Perceptron, but our method achieves the correct middle ground.

>>>>

%%some errors where DD picks the wrong model:
%%gold: 有 亭台樓閣 流水
%%CRF: 亭台 樓閣  <-- DD
%%PCT: 亭台樓閣
%\begin{small}
%\begin{tabbing}
%\ \ \ \ \= \emph{Gloss}\ \ \ \ \= Large-scale / sea, land, and air / \\ 
%\> \> joint / military exercises\\
%\> \emph{Gold}\> 大规模 / 海陆空 / 联合 / 军演\\
%
%\> \emph{CRF}\> 大规模 / 海 / 陆空 / 联合 / 军演\\
%
%\> \emph{PCPT}\> 大规模 / 海陆空 / 联合 / 军演\\
%
%\> \emph{DD}\> 大规模 / 海 / 陆空 / 联合 / 军演\\
%\end{tabbing}
%\end{small}
In many cases the relative confidence of each model means that dual decomposition is capable of using information from both sources to generate a series of correct segmentations better than either baseline model alone. The example below shows a difficult-to-segment proper name comprised of common characters, which results in undersegmentation by the character-based CRF and oversegmentation by the word-based perceptron, but our method achieves the correct middle ground.

### 2013-07-06 cws/emnlp_cws/experiment.tex
removed stats-sig descriptions
a bunch of final minor changes

We conduct experiments on the SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets to evaluate the effectiveness of the proposed dual decomposition algorithm. We use the publicly available Stanford CRF segmenter \cite{Tseng:2005:SIGHAN}\footnote{http://nlp.stanford.edu/software/segmenter.shtml} as our character-based baseline model, and reproduce the perceptron-based segmenter from \newcite{Zhang:2007:ACL} as our word-based baseline model.
We adopted the development setting from \cite{Zhang:2007:ACL}, and used CTB sections 1-270 for training, and sections 400-931for development. The optimized hyper-parameters used are: $\ell_{2}$ regularization parameter $\lambda$ in CRF is set to $3$; perceptron is trained for 10 iterations with beam size 200; dual decomposition is run to max iteration ($T$ in Algo.~\ref{algo:DD}) of 100 with step size ($\alpha_t$ in Algo.~\ref{algo:DD}) 0.1. Other than the standard precision (P), recall (R) and F$_1$ scores, we also evaluate segmentation consistency as proposed by \cite{Chang:2008:ACL}, who have shown that increased segmentation consistency is correlated with better machine translation performance. The consistency measure calculates the entropy of segmentation variations --- the lower the score the better. Statistical significance tests are done using the paired bootstrap resampling method \cite{efron93bootstrap}.

>>>>

We conduct experiments on the SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets to evaluate the effectiveness of the proposed dual decomposition algorithm. We use the publicly available Stanford CRF segmenter \cite{Tseng:2005:SIGHAN}\footnote{http://nlp.stanford.edu/software/segmenter.shtml} as our character-based baseline model, and reproduce the perceptron-based segmenter from \newcite{Zhang:2007:ACL} as our word-based baseline model.
We adopted the development setting from \cite{Zhang:2007:ACL}, and used CTB sections 1-270 for training, and sections 400-931for development. The optimized hyper-parameters used are: $\ell_{2}$ regularization parameter $\lambda$ in CRF is set to $3$; perceptron is trained for 10 iterations with beam size 200; dual decomposition is run to max iteration of 100 ($T$ in Algo.~\ref{algo:DD}) with step size 0.1 ($\alpha_t$ in Algo.~\ref{algo:DD}). Other than the standard precision (P), recall (R) and F$_1$ scores, we also evaluate segmentation consistency as proposed by \cite{Chang:2008:ACL}, who have shown that increased segmentation consistency is correlated with better machine translation performance. The consistency measure calculates the entropy of segmentation variations --- the lower the score the better. 
%Statistical significance tests are done using the paired bootstrap resampling method \cite{efron93bootstrap}.

### 2013-07-06 cws/emnlp_cws/introduction.tex
a bunch of final minor changes

%Third paragraph: 
There are two primary classes of models: character-based \cite{Xue:2003:IJCLCLP,Tseng:2005:SIGHAN,Zhang:2006:HLT-NAACL,Wang:2010:COLING} and word-based \cite{Andrew:2006:EMNLP,Zhang:2007:ACL}, with corresponding advantages and disadvantages. \newcite{Sun:2010:COLING} details their theoretical distinctions: character-based approaches better model the internal compositional structure of words and are therefore more effective at inducing new \textsc{oov} words; word-based approaches are better at reproducing the words of the training lexicon and can capture information from significantly larger contextual spans. Prior work has shown performance gains from combining these two types of models to exploit their respective strengths, but such approaches are often complex to implement and computationally expensive.
% too detailed?
%Due to the Markov assumption of the linear-chain CRFs that are commonly used in character-based segmentation the models typically only have information about the immediately neighboring characters, while word-based methods tend to capture information from significantly larger contextual spans.
%An additional advantage of word-segmenter is that they can explore larger context than character-based models (this is a little hard to explain without getting into the details of how these models work, maybe leave this piece till later; the basic idea is that character-based models -- i.e., linear-chain CRFs --- have very limited context due to Markov assumption, it typically only have direct information about the immediate neighboring characters, although information from longer-range context does flow because of the sentence-level normalization, its effect is much less direct. Word-based models in contrary directly captures the formation of entire words, say the previous word token has 3 characters, and the current word being considered has 3 characters, then a word-level bigram feature would capture context in neighboring 6 characters.

In this work, we propose a simple and principled joint decoding method for combining character-based and word-based segmenters based on dual decomposition. This method has strong optimality guarantees and works very well empirically. It is easy to implement and does not require retraining of existing character- and word-based segmenters.
Experimental results on standard SIGHAN 2003 and 2005 bake-off evaluations show that our model outperforms the character and word baselines by a significant margin.
In particular, it improves \textsc{oov} recall rates and segmentation consistency, % this is now validated
and gives the best reported results to date on 6 out of 7 datasets.

>>>>

%Third paragraph: 
There are two primary classes of models: character-based, where the foundational units for processing are individual Chinese characters \cite{Xue:2003:IJCLCLP,Tseng:2005:SIGHAN,Zhang:2006:HLT-NAACL,Wang:2010:COLING}, and word-based, where the units are full words based on some dictionary or training lexicon \cite{Andrew:2006:EMNLP,Zhang:2007:ACL}. \newcite{Sun:2010:COLING} details their respective theoretical strengths: character-based approaches better model the internal compositional structure of words and are therefore more effective at inducing new \textsc{oov} words; word-based approaches are better at reproducing the words of the training lexicon and can capture information from significantly larger contextual spans. Prior work has shown performance gains from combining these two types of models to exploit their respective strengths, but such approaches are often complex to implement and computationally expensive.
% too detailed?
%Due to the Markov assumption of the linear-chain CRFs that are commonly used in character-based segmentation the models typically only have information about the immediately neighboring characters, while word-based methods tend to capture information from significantly larger contextual spans.
%An additional advantage of word-segmenter is that they can explore larger context than character-based models (this is a little hard to explain without getting into the details of how these models work, maybe leave this piece till later; the basic idea is that character-based models -- i.e., linear-chain CRFs --- have very limited context due to Markov assumption, it typically only have direct information about the immediate neighboring characters, although information from longer-range context does flow because of the sentence-level normalization, its effect is much less direct. Word-based models in contrary directly captures the formation of entire words, say the previous word token has 3 characters, and the current word being considered has 3 characters, then a word-level bigram feature would capture context in neighboring 6 characters.

In this work, we propose a simple and principled joint decoding method for combining character-based and word-based segmenters based on dual decomposition. This method has strong optimality guarantees and works very well empirically. It is easy to implement and does not require retraining of existing character- and word-based segmenters.
Experimental results on standard SIGHAN 2003 and 2005 bake-off evaluations show that our model outperforms the character and word baselines by a significant margin.
In particular, out approach improves \textsc{oov} recall rates and segmentation consistency, % this is now validated
and gives the best reported results to date on 6 out of 7 datasets.

### 2013-07-06 cws/emnlp_cws/models.tex
a bunch of final minor changes

In this section, we describe the character-based and word-based models we use as baselines, and review existing approaches to combine these models.

\subsection{Character-based Models}
In the most commonly used contemporary approach to character-based segmentation, first proposed by \cite{Xue:2003:IJCLCLP}, CWS is seen as a character sequence tagging task, where each character is tagged on whether it is at the beginning, middle, or end of a word. Conditional random fields (CRF) \cite{Lafferty:2001:ICML} are widely adopted for this task, and give state-of-the-art results \cite{Tseng:2005:SIGHAN}. In a first-order linear-chain CRF model, the conditional probability of a label sequence $\mathbf{y}$ given a word sequence $\mathbf{x}$ is defined as:
\begin{align*}\vspace{-10em}
P(\mathbf{y} | \mathbf{x}) = \frac{1}{Z}{ \sum\limits_{t=1}^{|\mathbf{y}|}{ \exp\left( \theta \cdot {f}(x, y_t, y_{t+1}) \right) }}
\vspace{-10em}
\end{align*}
\noindent $f(x, y_{t}, y_{t-1})$ are feature functions that typically include surrounding n-gram and morphological suffix/prefix features. These types of features capture the compositional properties of characters and are likely to generalize well to unknown words.  
However, the Markov assumption in CRF limits the context of such features; it is difficult to capture long-range word features in this model. 
%, which is important for admitting efficient inference, restricts the CRF to very local context features. A first-order CRF can only reason about character boundary decisions of current and neighboring positions. 
%It is therefore difficult to directly model words of greater length. Although higher-order CRF could potentially alleviate this problem, and has been applied to CWS \cite{Zhao:2007:ICNC}, it comes at the cost of exponentially higher model complexity.

@@

Dual decomposition (DD) \cite{Rush:2010:EMNLP} offers an attractive framework for combining these two types of models without incurring high costs in model complexity (in contrast to \cite{Sun:2009:HLT-NAACL}) or decoding efficiency (in contrast to bagging in \cite{Wang:2006:SIGHAN,Sun:2010:COLING}). DD has been successfully applied to similar situations for combining local with global models; for example, in dependency parsing \cite{Koo:2010:EMNLP}), bilingual sequence tagging \cite{Wang:2013:ACL} and word alignment \cite{Denero:2011:ACL}.

>>>>

In this section, we describe the character-based and word-based models we use as baselines, review existing approaches to combination, and describe our algorithm for joint decoding with dual decomposition.

\subsection{Character-based Models}
In the most commonly used contemporary approach to character-based segmentation, first proposed by \cite{Xue:2003:IJCLCLP}, CWS is seen as a character sequence tagging task, where each character is tagged on whether it is at the beginning, middle, or end of a word. Conditional random fields (CRF) \cite{Lafferty:2001:ICML} have been widely adopted for this task, and give state-of-the-art results \cite{Tseng:2005:SIGHAN}. In a first-order linear-chain CRF model, the conditional probability of a label sequence $\mathbf{y}$ given a word sequence $\mathbf{x}$ is defined as:
\begin{align*}\vspace{-10em}
P(\mathbf{y} | \mathbf{x}) = \frac{1}{Z}{ \sum\limits_{t=1}^{|\mathbf{y}|}{ \exp\left( \theta \cdot {f}(x, y_t, y_{t+1}) \right) }}
\vspace{-10em}
\end{align*}
\noindent $f(x, y_{t}, y_{t-1})$ are feature functions that typically include surrounding character n-gram and morphological suffix/prefix features. These types of features capture the compositional properties of characters and are likely to generalize well to unknown words.  
However, the Markov assumption in CRF limits the context of such features; it is difficult to capture long-range word features in this model. 
%, which is important for admitting efficient inference, restricts the CRF to very local context features. A first-order CRF can only reason about character boundary decisions of current and neighboring positions. 
%It is therefore difficult to directly model words of greater length. Although higher-order CRF could potentially alleviate this problem, and has been applied to CWS \cite{Zhao:2007:ICNC}, it comes at the cost of exponentially higher model complexity.

@@

Dual decomposition (DD) \cite{Rush:2010:EMNLP} offers an attractive framework for combining these two types of models without incurring high costs in model complexity (in contrast to \cite{Sun:2009:HLT-NAACL}) or decoding efficiency (in contrast to bagging in \cite{Wang:2006:SIGHAN,Sun:2010:COLING}). DD has been successfully applied to similar situations for combining local with global models; for example, in dependency parsing \cite{Koo:2010:EMNLP}, bilingual sequence tagging \cite{Wang:2013:ACL} and word alignment \cite{Denero:2011:ACL}.
